%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Organisation
    {E-Class - An Online Education Platform} % Project
    {Apr 2023 - Present} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of project
        \item {An online class application that allows teachers to connect remotely with students. This is an ongoing project.}
        \item {The project is built using NextJs and uses MongoDB database to persist data.}
        \item {\textbf{Tech Used:} HTML/CSS, TypeScript, NextJs, MongoDB, Prisma, RestAPI.}
        \item {\textbf{Github Link:} \href{https://github.com/Rafael00X/E-Class}{github.com/Rafael00X/E-Class}}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {} % Organisation
    {Ecommerce Website} % Project
    {Dec 2022 - Feb 2023} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of project
        \item {An e-commerce website built using full-stack web development technologies. The website allows users to browse products and services online.}
        \item {The project consists of one frontend application built using ReactJs, and two backend restful services built using Spring Boot.}
        \item {The project uses MySQL database to store and persist data.}
        \item {\textbf{Tech Used:} HTML/CSS, JavaScript, ReactJs, Java, Spring Boot, Spring Data JPA, MySQL, JUnit, Mockito, RestAPI.}
        \item {\textbf{Github Link:} \href{https://github.com/Rafael00X/Ecommerce-Frontend}{github.com/Rafael00X/Ecommerce-Frontend}}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {} % Organisation
    {Notechat - A Social Media Platform} % Project
    {Oct 2021 - Jan 2022} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of project
        \item {A simple social media web application built using full-stack technology. Users can share posts, like and comment, or engage in real-time chat with other users in their contacts.}
        \item {The project consists of one frontend application built using ReactJs, and one backend service built using NodeJs.}
        \item {The project uses MongoDB database to store and persist data.}
        \item {\textbf{Tech Used:} HTML/CSS, JavaScript, ReactJs, NodeJs, MongoDB, Mongoose, SocketIO, GraphQL, Apollo Server/Client.}
        \item {\textbf{Github Link:} \href{https://github.com/Rafael00X/NoteChat-Frontend}{github.com/Rafael00X/NoteChat-Frontend}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
